Convergence rate of MAP estimates \\ for the exponential family

### 2021-05-10 main.tex
Separate theorem and proof for gaussian variance

\begin{example}
	For $\cN(0,\sigma^2)$, both the entropy and the log-partition are roughly negative logarithm $z\mapsto - \log(z)$. Which yields the same shape of Bregman divergence, as visible below (all three lines are equal)
\begin{align}
	\KL( \sigma_n^2 ; \sigma_*^2) 
	&= \half \left ( \frac{\sigma_*^2}{ \sigma_n^2} - 1 - \log \frac{\sigma_*^2}{ \sigma_n^2} \right) \\
	\bregmanconj( \mu_*; \mu_n) 
	&= \half \left ( \frac{\mu_*}{ \mu_n} - 1 - \log  \frac{\mu_*}{ \mu_n} \right) \\
	\bregman( \natp_n; \natp_* ) 
	&=  \half \left ( \frac{ \natp_n}{\natp_*} - 1 - \log  \frac{ \natp_n}{\natp_*} \right) \; .
\end{align}
In other words, this divergence measures the discrepancy between the ratio $\frac{ \natp_n}{\natp_*} =  \frac{\mu_*}{ \mu_n}  $ and $1$ via the function $\phi$
\begin{align}
	\phi(z) := \half (z - 1 - \log(z)) \\
	\bregman( \natp_n; \natp_* )   = \phi(\frac{ \natp_n}{\natp_*}) =  \phi(\frac{\mu_*}{ \mu_n})
\end{align}
as illustrated in Figure~\ref{fig:phi}. We can get a non-transcendental upper bound thanks to the inequality
\begin{align}
	1 - \inv{z} \leq \log(z) 
	\label{eq:log_bound}\\
	\implies \phi(z) &\leq \half (z + \inv{z}) - 1 = \frac{(z-1)^2}{2 z}
\end{align}
as illustrated in Figure~\ref{fig:phi}.
\end{example}

@@

\begin{example}
	\paragraph{MLE exact computation}
	The MLE of $\cN(0,\mu_*)$ is $\mu_n = \sum_i X_i^2 /n$. The ratio to the optimum  $\frac{\mu_n}{\mu_*}$follows a \href{https://en.wikipedia.org/wiki/Chi-square_distribution}{Chi-square distribution} with $n$ degrees of freedom $\chi^2(n)$ divided by $n$. Its inverse $\frac{\mu_*}{ \mu_n} $ follows an \href{https://en.wikipedia.org/wiki/Inverse-chi-squared_distribution}{inverse Chi-square distribution} with expectation 
	\begin{align}
		\expect{\frac{\mu_*}{ \mu_n}  - 1} 
		= \expect{\frac{n}{\chi^2(n)} - 1} =
		\begin{cases}
			\frac{n}{n-2} -1 = \frac{2}{n-2} \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Chi-squared\citep{pav2015moments}
	\begin{align}
		\expect{\log \frac{\mu_n}{\mu_*}} = \psi(\half[n]) - \log(\half[n])
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \mu_n) }
	&= \half \expect{\frac{\mu_*}{ \mu_n} - 1 + \log \left(\frac{\mu_n}{\mu_*} \right) } \\
	& =
	\begin{cases}
		\half \left ( \frac{2}{n-2} +\psi(\half[n]) - \log(\half[n]) \right )  \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	It is surprising that we need more than $3$ samples for the loss to have a bounded expectation. 
	It is also very pleasant that the optimal value $\mu_*$ does not appear in this rate, so that the convergence rate is independent of the actual solution.
	When the expectation is finite, we can make its formula intelligible thanks to \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function}
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x}	\; .
	\end{align}
	  For $n\geq 3$,
	\begin{align}
		\inv{n-2} - \inv{n}
		&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
		\leq \inv{n-2} - \inv{2 n} \\
		\iff
			\frac{2}{n(n-2)}
			&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
			\label{eq:tight_bounds}
	\end{align}
	so we get a $O(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	Using the \href{https://en.wikipedia.org/wiki/Digamma_function#Recurrence_formula_and_characterization}{Stirling series}, we can also get an asymptotic approximation
	\begin{align}
		\expect{\bregmanconj( \mu_*; \mu_n) }
		\in \inv{2n} + \frac{11}{6 n^2} + \frac{4}{n^2(n-2)} + O(n^{-4}) \; .
	\end{align}
	Unfortunately, formulas for the MAP seem to be much less nice. There is also a closed form for the multivariate generalization, thanks to the \href{https://en.wikipedia.org/wiki/Inverse-Wishart_distribution}{inverse Wishart distribution} and the \href{https://en.wikipedia.org/wiki/Wishart_distribution#Log-expectation}{expectation of the log-determinant of a Wishart}. Again the expected value is infinite whenever $n \leq d+1$ where $d$ is the dimension. We do not perform these calculations for now as we want to focus on the simplest possible examples.
\end{example}

\begin{example}
	\paragraph{MAP upper bound.}
	Wolfram finds no closed form for $\expect{\log\frac{\MAPm}{\mu^*}}$ but it does for $\expect{\frac{\mu^*}{\MAPm}} = \expect{\frac{\MAPt}{\natp^*}}$. 
	To start, let us plug in the definition of $\MAPm$
	\begin{align}
		\E[\MAPt] &= -\frac{n+n_0}{2}\expect{\inv{n_0 \mu_0 + \sum_i X_i^2}}  \\
		&= -\frac{n+n_0}{2 \mu^*}\expect{\inv{n_0 \frac{\mu_0}{\mu^*}+ \sum_i \frac{X_i^2}{ \mu^*} }} \\
		&= -\frac{n+n_0}{2 \mu^*}\expect{\inv{a + \chi^2(n)}}
	\end{align}
	where $\sum_i \frac{X_i^2}{ \mu^*}$ is a chi-square random variable of degree $n$ and 
	\begin{align}
			a=n_0 \frac{\mu_0}{\mu^*} \; .
	\end{align}
	This expectations is not simple to solve, but using wolfram, we get  the formula :
	\begin{align}
		\expect{\inv{a + \chi^2(n)}}  = \half e^{\frac{a}{2}} E_{\half[n]}(\half[a])
		\label{eq:wolfram_input}
	\end{align}
	where the \href{https://dlmf.nist.gov/8.19}{generalized exponential integral function} is defined as 
	\begin{align}
		E_k(z) = \int_1^\infty \frac{e^{-z t} }{t^k} dt \; .
	\end{align}
	Now our goal is to bound this function with simpler functions.
	Fortunately, mathematicians have been working on these integrals for decades.
	When $n=2$, we have the simple exponential integral function which \href{https://dlmf.nist.gov/6.8#E1}{verifies the bound}
	\begin{align}
		\half \log(1 + \frac{2}{x}) 
		\leq e^x E_1(x) 
		\leq \log(1+\inv{x}) \leq \inv{x} \; .
	\end{align}
	For larger $n$, we have \href{https://dlmf.nist.gov/8.19#E21}{the general bound}
	\begin{align}
		\inv{x+n}
		\leq e^x E_k(x) 
		\leq \inv{x + k - 1}
	\end{align}
	so that 
	\begin{align}
		\inv{a+n}
		\leq \expect{\inv{a + \chi^2(n)}}
		\leq \inv{a + n - 2}
	\end{align}
	so that
	\begin{align}
		\frac{n +n_0}{2 \mu^* (a + n)}	
		&\leq - \E[\MAPt]
		\leq \frac{n +n_0}{2 \mu^* (a + n - 2)}	\\
		\iff \inv{2 \mu_n}
		&\leq - \E[\MAPt]
		\leq \inv{2 \mu_n - \frac{4 \mu^*}{n + n_0}}	\\
		\iff \frac{\mu^*}{\mu_n}
		&\leq \expect{\frac{\mu^*}{\MAPm}} 
		\leq \frac{\mu^*}{\mu_n - \frac{4 \mu^*}{n + n_0}}  
		\label{eq:theta_expectation_bound}
	\end{align}
	because $\frac{\mu^* (a + n)}{n +n_0} = \mu_n$.
Now using the bound \eqref{eq:log_bound} on the logarithm, we get
\begin{align}
	2\expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \expect{\frac{\mu^*}{\MAPm}}  + \expect{\frac{\MAPm}{\mu^*}} - 1 \\
	&\leq \frac{\mu^*}{\mu_n - \frac{4 \mu^*}{n + n_0}}   + \frac{\mu_n}{\mu^*} - 1 \\
	&= \frac{n_0 + n}{a +n - 2} + \frac{a+n}{n_0 + n} - 2 \\
	&= \frac{n_0 - a + 2}{a +n - 2} + \frac{a - n_0}{n_0 + n} \\
	&= \frac{2}{a+n-2} + \frac{(n_0 - a)^2}{(a+n-2)(n_0 + n)} \\
	\implies \expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \frac{1}{a+n-2} + \frac{(n_0 - a)^2}{2(a+n-2)(n_0 + n)} 
\end{align}
where recall that $a=n_0\frac{\mu_0}{\mu^*}$. 
This inequality highlights a clear variance-bias decomposition, to compare with the MLE. Unfortunately it is not tight asymptotically as the inequality \eqref{eq:log_bound} is far from tight. We are basically losing a factor 2 compared to $1/2n$.

\paragraph{MLE Loose Upper Bound.}
If we apply \eqref{eq:log_bound} to the MLE instead, we get the upper bound
\begin{align}
	\expect{\bregmanconj(\mu^*; \MAPm^\text{MLE})}
	&\leq  \half \left( \expect{\frac{n}{\chi^2(n)}} + \expect{\frac{\chi^2(n)}{n}} - 2 \right ) \\
	&= \half \left( \frac{n}{n-2} + 1 - 2 \right)  
	= \frac{1}{n-2}
\end{align}
which is exactly $1/2n$ larger than \eqref{eq:tight_bounds} which we got thanks to an exact computation of the expectation of the log term, and a tight upper bound on the digamma function.
\end{example}

	\begin{figure}[ht]
    	\centering
	    \includegraphics[width=.7\textwidth]{figs/wolfram.png}
	    \caption{Output of Wolfram when queried for the integral \eqref{eq:wolfram_input}}
    	\label{fig:wolfram}
	\end{figure}

@@

\section{Optimization Perspective}
\paragraph{Problem.}
Our goal is to solve the following problem
\begin{align}
	\min_\natp f(\natp) := -\langle \mu^* ; \natp \rangle + \logpart(\natp)
\end{align}
where $\logpart$ is a convex function and we only have access to stochastic oracles $X \sim p(X | \natp^*)$, meaning we can compute stochastic values and gradients 
\begin{align}
	f(\natp ; X) &= -\langle T(X) ; \natp \rangle + \logpart(\natp) \\
	\nabla f(\natp ; X) &= A(\natp) - T(X)
\end{align}
such that $T(X) = \mu^*$.

>>>>

\begin{example}
	For $\cN(0,\sigma^2)$, both the entropy and the log-partition are roughly negative logarithm $z\mapsto - \log(z)$. Which yields the same shape of Bregman divergence, as visible below (all three lines are equal)
\begin{align}
	\KL( \sigma_*^2 ; \sigma_n^2 ) 
	&= \half \left ( \frac{\sigma_*^2}{ \sigma_n^2} - 1 - \log \frac{\sigma_*^2}{ \sigma_n^2} \right) \\
	\bregmanconj( \mu_*; \mu_n) 
	&= \half \left ( \frac{\mu_*}{ \mu_n} - 1 - \log  \frac{\mu_*}{ \mu_n} \right) \\
	\bregman( \natp_n; \natp_* ) 
	&=  \half \left ( \frac{ \natp_n}{\natp_*} - 1 - \log  \frac{ \natp_n}{\natp_*} \right) \; .
\end{align}
In other words, this divergence measures the discrepancy between the ratio $\frac{ \natp_n}{\natp_*} =  \frac{\mu_*}{ \mu_n}  $ and $1$ via the function $\phi$
\begin{align}
	\phi(z) := \half (z - 1 - \log(z)) \\
	\bregman( \natp_n; \natp_* )   = \phi(\frac{ \natp_n}{\natp_*}) =  \phi(\frac{\mu_*}{ \mu_n})
\end{align}
as illustrated in Figure~\ref{fig:phi}. We can get a non-transcendental upper bound thanks to the inequality
\begin{align}
	1 - \inv{z} &\leq \log(z) 
	\label{eq:log_bound}\\
	\implies \phi(z) &\leq \half (z + \inv{z}) - 1 = \frac{(z-1)^2}{2 z}
\end{align}
as illustrated in Figure~\ref{fig:phi}.
\end{example}

@@

\begin{example}
	\begin{theorem}[MLE tight upper bound]
	The MLE of $\cN(0,\mu_*)$ is $\hat \mu_n^\text{MLE} = \inv{n} \sum_i X_i^2 $.
	Its expected suboptimality is infinite when $n\leq 2$, and otherwise upper-bounded as
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \hat \mu_n^\text{MLE}) }
			\leq \inv{2n} +\frac{2}{n(n-2)} \; .
			\label{eq:tight_bounds}
	\end{align}
\end{theorem}
Note that this upper bound is asymptotically tight.
 There is also a closed form for the multivariate generalization, thanks to the \href{https://en.wikipedia.org/wiki/Inverse-Wishart_distribution}{inverse Wishart distribution} and the \href{https://en.wikipedia.org/wiki/Wishart_distribution#Log-expectation}{expectation of the log-determinant of a Wishart}. The expected value is infinite whenever $n \leq d+1$ where $d$ is the dimension. We do not perform these calculations for now as we want to focus on the simplest possible examples.

As for the MAP, we did not manage to get an asymptotically tight upper bound. Nevertheless, using inequality~\eqref{eq:log_bound}, we did get an interesting upper bound. 
To start, let us recall that the MAP of $\cN(0,\mu_*)$ is $\hat \mu_n = \frac{n_0 \mu_0 + \sum_i X_i^2}{n_0 + n}$.
Its expectation is simply $\mu_n= \frac{n_0 \mu_0 + n \mu^*}{n_0 + n}$.
We now present a lemma on its expected inverse.
\begin{lemma}[Expected MAP natural parameter]
	The expectation of the natural parameter of the MAP of $\cN(0,\mu_*)$ is bounded as
	\begin{align}
		\frac{\mu^*}{\mu_n}
		\leq \expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		\leq \frac{1}{\frac{\mu_n}{\mu^*} - \frac{2}{n+n_0}} \; .
	\end{align}
\end{lemma}
Using this lemma, along with~\eqref{eq:log_bound}, we get the following result.
\begin{theorem}[MAP Upper Bound]
 The expected suboptimality of the MAP of $\cN(0,\mu^*)$ with prior hyper-parameters $(n_0,\mu_0)$ is 
\begin{equation}
	\expect{\bregmanconj( \mu_*; \hat \mu_n^\text{MAP})}
	\leq \begin{cases}
		\bregmanconj( \mu_*; \mu_0) \ \text{ if } \ n=0, \\
		\frac{1+n_0}{4} e^{\half[a]} \sqrt{\frac{2 \pi}{a}} \mathrm{erfc}(\sqrt{\half[a]})  - \half  + \frac{a - n_0}{2(1+n_0)} \ \text{if}\ n=1,\\
		\frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} if n\geq 2 \ \text{and}\ a=n_0 \frac{\mu_0}{\mu^*} >0
	\end{cases}
\end{equation}
\end{theorem}

\begin{proof}
	Wolfram finds no closed form for $\expect{\log\frac{\MAPm}{\mu^*}}$ but it does for $\expect{\frac{\mu^*}{\MAPm}} = \expect{\frac{\MAPt}{\natp^*}}$. 
	To start, let us plug in the definition of $\MAPm$
	\begin{align}
		\expect{\frac{\mu^*}{\MAPm}} 
		= \expect{\frac{\MAPt}{\natp^*}} 
		&= expect{\frac{(n_0+n) \mu^*}{n_0 \mu_0 + \sum_i X_i^2}}  \\
		&= (n_0 + n) \expect{\inv{n_0 \frac{\mu_0}{\mu^*}+ \sum_i \frac{X_i^2}{ \mu^*} }} \\
		&= (n_0 +n) \expect{\inv{a + \chi^2(n)}}
	\end{align}
	where $\chi^2(n) = \sum_i \frac{X_i^2}{ \mu^*}$ is a chi-square random variable of degree $n$ and 
	\begin{align}
			a=n_0 \frac{\mu_0}{\mu^*} \; .
	\end{align}
	This expectations is not simple to solve, but using the trick
	\begin{align}
		&\int_1^\infty e^{-\frac{zt}{2}} dt = \frac{2}{z} e^{-\half[z]} 
		\ \implies \ \inv{z} = \half e^{\half[z]} \int_1^\infty e^{-\frac{zt}{2}} dt
		\\
		\implies 
		&\inv{a+x} = \half e^{\frac{a+x}{2}} \int_1^\infty e^{- \frac{(a+x)t}{2}}dt \; ,
	\end{align} 
	we get  the formula :
	\begin{align}
		(n_0 +n) \expect{\inv{a + \chi^2(n)}}  = \half[n_0+n] e^{\frac{a}{2}} E_{\half[n]}(\half[a])
		\label{eq:wolfram_input}
	\end{align}
	where the \href{https://dlmf.nist.gov/8.19}{generalized exponential integral function} is defined as 
	\begin{align}
		E_k(z) = \int_1^\infty \frac{e^{-z t} }{t^k} dt \; .
	\end{align}
	Now our goal is to bound this function with simpler functions.
	Fortunately, mathematicians have been working on these integrals for decades.
	When $n=2$, we have the simple exponential integral function which \href{https://dlmf.nist.gov/6.8\#E1}{verifies the bound}
	\begin{align}
		\half \log(1 + \frac{2}{x}) 
		\leq e^x E_1(x) 
		\leq \log(1+\inv{x}) \leq \inv{x} \; .
	\end{align}
	or 
	\begin{align}
		E_{\half[1]}(\half[a]) = \sqrt{\frac{a}{2\pi}}
	\end{align}
	For larger $n$, we have \href{https://dlmf.nist.gov/8.19\#E21}{the general bound}
	\begin{align}
		\inv{x+k}
		\leq e^x E_k(x) 
		\leq \inv{x + k - 1}
	\end{align}
	so that 
	\begin{align}
		\inv{a+n}
		\leq \expect{\inv{a + \chi^2(n)}}
		\leq \inv{a + n - 2}
	\end{align}
	so that
	\begin{align}
		\frac{n +n_0}{2 \mu^* (a + n)}	
		&\leq - \E[\MAPt]
		\leq \frac{n +n_0}{2 \mu^* (a + n - 2)}	\\
		\iff \inv{2 \mu_n}
		&\leq - \E[\MAPt]
		\leq \inv{2 \mu_n - \frac{4 \mu^*}{n + n_0}}	\\
		\iff \frac{\mu^*}{\mu_n}
		&\leq \expect{\frac{\mu^*}{\MAPm}} 
		\leq \frac{\mu^*}{\mu_n - \frac{2 \mu^*}{n + n_0}}  
		\label{eq:theta_expectation_bound}
	\end{align}
	because $\frac{\mu^* (a + n)}{n +n_0} = \mu_n$.
Now using the bound \eqref{eq:log_bound} on the logarithm, we get
\begin{align}
	2\expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \expect{\frac{\mu^*}{\MAPm}}  + \expect{\frac{\MAPm}{\mu^*}} - 1 \\
	&\leq \frac{\mu^*}{\mu_n - \frac{2 \mu^*}{n + n_0}}   + \frac{\mu_n}{\mu^*} - 1 \\
	&= \frac{n_0 + n}{a +n - 2} + \frac{a+n}{n_0 + n} - 2 \\
	&= \frac{n_0 - a + 2}{a +n - 2} + \frac{a - n_0}{n_0 + n} \\
	&= \frac{2}{a+n-2} + \frac{(n_0 - a)^2}{(a+n-2)(n_0 + n)} \\
	\implies \expect{\bregmanconj(\mu^*; \MAPm)} 
	&\leq \frac{1}{a+n-2} + \frac{(n_0 - a)^2}{2(a+n-2)(n_0 + n)} \\
	&\leq \frac{1}{a+n-2} + \frac{\half(1 - \frac{\mu_0}{\mu^*})^2}{(\frac{\mu_0}{\mu^*}+\frac{n-2}{n_0})(1 + \frac{n}{n_0} )} 
\end{align}
where recall that $a=n_0\frac{\mu_0}{\mu^*}$. 
This inequality highlights a clear variance-bias decomposition, to compare with the MLE. Unfortunately it is not tight asymptotically as the inequality \eqref{eq:log_bound} is not quadratically tight around $1$. We are basically losing a factor 2 compared to $1/2n$. 
\end{proof}

\end{example}

\section{Proofs for Gaussian Variance}
\subsection{MLE Tight Upper Bound}
	\begin{theorem}[MLE tight upper bound]
	The MLE of $\cN(0,\mu_*)$ is $\mu_n = \inv{n} \sum_i X_i^2 $.
	Its expected suboptimality is infinite when $n\leq 2$ and 
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
	\end{align}
	otherwise. Note that this upper bound is asymptotically tight.
	\end{theorem}

	\begin{proof}
	The ratio to the optimum  $\frac{\mu_n}{\mu_*}$follows a \href{https://en.wikipedia.org/wiki/Chi-square_distribution}{Chi-square distribution} with $n$ degrees of freedom $\chi^2(n)$ divided by $n$. Its inverse $\frac{\mu_*}{ \mu_n} $ follows an \href{https://en.wikipedia.org/wiki/Inverse-chi-squared_distribution}{inverse Chi-square distribution} with expectation 
	\begin{align}
		\expect{\frac{\mu_*}{ \mu_n}  - 1} 
		= \expect{\frac{n}{\chi^2(n)} - 1} =
		\begin{cases}
			\frac{n}{n-2} -1 = \frac{2}{n-2} \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Chi-squared\citep{pav2015moments}
	\begin{align}
		\expect{\log \frac{\mu_n}{\mu_*}} = \psi(\half[n]) - \log(\half[n])
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \mu_n) }
	&= \half \expect{\frac{\mu_*}{ \mu_n} - 1 + \log \left(\frac{\mu_n}{\mu_*} \right) } \\
	& =
	\begin{cases}
		\half \left ( \frac{2}{n-2} +\psi(\half[n]) - \log(\half[n]) \right )  \ \text{ if } n>2, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	It is surprising that we need more than $3$ samples for the loss to have a bounded expectation. 
	It is also very pleasant that the optimal value $\mu_*$ does not appear in this rate, so that the convergence rate is independent of the actual solution.
	When the expectation is finite, we can make its formula intelligible thanks to \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function}
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x}	\; .
	\end{align}
	  For $n\geq 3$,
	\begin{align}
		\inv{n-2} - \inv{n}
		&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
		\leq \inv{n-2} - \inv{2 n} \\
		\iff
			\frac{2}{n(n-2)}
			&\leq \expect{\bregmanconj( \mu_*; \mu_n) }
			\leq \inv{2n} +\frac{2}{n(n-2)}
	\end{align}
	so we get a $O(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	\end{proof}

	Using the \href{https://en.wikipedia.org/wiki/Digamma_function#Recurrence_formula_and_characterization}{Stirling series}, we can also get an asymptotic approximation
	\begin{align}
		\expect{\bregmanconj( \mu_*; \mu_n) }
		\in \inv{2n} + \frac{11}{6 n^2} + \frac{4}{n^2(n-2)} + O(n^{-4}) \; .
	\end{align}

\subsection{MLE Loose Upper Bound}
If we apply \eqref{eq:log_bound} to the MLE, we get the upper bound
\begin{align}
	\expect{\bregmanconj(\mu^*; \MAPm^\text{MLE})}
	&\leq  \half \left( \expect{\frac{n}{\chi^2(n)}} + \expect{\frac{\chi^2(n)}{n}} - 2 \right ) \\
	&= \half \left( \frac{n}{n-2} + 1 - 2 \right)  
	= \frac{1}{n-2}
\end{align}
which is exactly  an additive term $1/2n$ larger than \eqref{eq:tight_bounds}. This highlights the factor $2$ difference between the log-bound and an exact computation of the expectation of the log term, and a tight upper bound on the digamma function.

@@

\section{Optimization Perspective}
\paragraph{Problem.}
Our goal is to solve the following problem
\begin{align}
	\min_\natp \E[f(\natp ; X)] := -\langle \E[T(X)] ; \natp \rangle + \logpart(\natp)
\end{align}
where $\logpart$ is a convex function and we only have access to stochastic oracles $X \sim p(X | \natp^*)$, meaning we can compute stochastic values and gradients 
\begin{align}
	f(\natp ; X) &= -\langle T(X) ; \natp \rangle + \logpart(\natp) \\
	\nabla f(\natp ; X) &= \nabla \logpart(\natp) - T(X)
\end{align}
such that $\E[T(X)] = \mu^*$.
